Novelty statement

### 2023-10-17 paper.qmd
Prep for submission

---
title: "CRUSE to Safe Cycling in Ireland"
subtitle: An Open Source Tool to Support Active Travel
bibliography: bibliography.bib
csl: apa.csl
editor:
  markdown:
    wrap: sentence
number-sections: true

# # Uncomment for draft versions:
format: 
  html: default
  # docx: default
# # # Uncomment for formatted version
#   elsevier-pdf:
#     linestretch: 2
#     keep-tex: true
#     journal:
#       name: European Transport Research Review
#       formatting: preprint
#       model: 3p
#       cite-style: super
# # #   # pdf: default

@@

::: {#fig-dublin}
![](images/paste-1.png)

![](images/paste-3.png)

@@

::: {#fig-trip-purposes}
![](images/paste-4.png)

@@

::: {#fig-route-types layout-nrow="2"}
![](images/naas_quietest_godutch.png){width="250"}

![](images/naas_fastest_godutch.png){width="250"}

![](images/newbridge_quietest_godutch.png){width="250"}

![](images/newbridge_fastest_godutch.png){width="250"}

@@

![](images/scenarios_kildare.png)

@@

```{mermaid}
%%| fig-width: 100%
%%| fig-cap: Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.
%%| label: fig-user-stories
graph LR
    A(Professional user) --> B[CRUSE landing page]
    B --> C[CRUSE national map]
    C --> D[CRUSE county map]
    D --> F[Full county map]
    D --> CS[County statistics]
    D --> Q[Quiet and fast route networks]
    D --> DD[Data downloads]
    DD --> EX{External tools}
    X(Non-professional user) --> Y[CRUSE landing page]
    Y --> Z[CRUSE national map]
    Z --> R[CRUSE county level results]
    Z --> E(Exploration)
    R --> E
    E --> COMS{Communication}
```

@@

::: {#fig-city-results}
![](images/rnet_types.png)

>>>>

---
title: "CRUSE to Safe Cycling in Ireland"
subtitle: An Open Source Tool to Support Active Travel
bibliography: bibliography.bib
csl: apa.csl
editor:
  markdown:
    wrap: sentence
number-sections: true
latex-clean: false
pdf-engine: pdflatex
knitr:
  opts_chunk:
    fig.path: images/
format: 
  # html: default
  # docx: default
# # # Uncomment for formatted version
  elsevier-pdf:
    linestretch: 2
    keep-tex: true
    journal:
      name: European Transport Research Review
      formatting: preprint
      model: 3p
      cite-style: super
# # #   # pdf: default

@@

::: {#fig-dublin}
![](paste-1.png)

![](paste-3.png)

@@

::: {#fig-trip-purposes}
![](paste-4.png)

@@

::: {#fig-route-types layout-nrow="2"}
![](naas_quietest_godutch.png){width="250"}

![](naas_fastest_godutch.png){width="250"}

![](newbridge_quietest_godutch.png){width="250"}

![](newbridge_fastest_godutch.png){width="250"}

@@

![](scenarios_kildare.png)

@@

```{r}
#| eval: false
#| echo: false
# ```{mermaid}
%%| eval: false
%%| fig-width: 100%
%%| fig-cap: Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.
%%| label: fig-user-stories
graph LR
    A(Professional user) --> B[CRUSE landing page]
    B --> C[CRUSE national map]
    C --> D[CRUSE county map]
    D --> F[Full county map]
    D --> CS[County statistics]
    D --> Q[Quiet and fast route networks]
    D --> DD[Data downloads]
    DD --> EX{External tools}
    X(Non-professional user) --> Y[CRUSE landing page]
    Y --> Z[CRUSE national map]
    Z --> R[CRUSE county level results]
    Z --> E(Exploration)
    R --> E
    E --> COMS{Communication}
```

::: {#fig-user-stories}

![](mermaid-figure-1.png)

Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.

:::

@@

::: {#fig-city-results}
![](rnet_types.png)

### 2023-10-17 paper.tex
Prep for submission

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\includegraphics{images/paste-1.png}

\includegraphics{images/paste-3.png}

@@

\includegraphics{images/paste-4.png}

@@

\includegraphics[width=2.60417in,height=\textheight]{images/naas_quietest_godutch.png}

@@

\includegraphics[width=2.60417in,height=\textheight]{images/naas_fastest_godutch.png}

@@

\includegraphics[width=2.60417in,height=\textheight]{images/newbridge_quietest_godutch.png}

@@

\includegraphics[width=2.60417in,height=\textheight]{images/newbridge_fastest_godutch.png}

@@

\includegraphics{images/scenarios_kildare.png}

@@

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-latex/mermaid-figure-1.png}

@@

\includegraphics{images/rnet_types.png}

>>>>

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, sharp corners, frame hidden, breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

\includegraphics{paste-1.png}

\includegraphics{paste-3.png}

@@

\includegraphics{paste-4.png}

@@

\includegraphics[width=2.60417in,height=\textheight]{naas_quietest_godutch.png}

@@

\includegraphics[width=2.60417in,height=\textheight]{naas_fastest_godutch.png}

@@

\includegraphics[width=2.60417in,height=\textheight]{newbridge_quietest_godutch.png}

@@

\includegraphics[width=2.60417in,height=\textheight]{newbridge_fastest_godutch.png}

@@

\includegraphics{scenarios_kildare.png}

@@

\includegraphics{mermaid-figure-1.png}

@@

\includegraphics{rnet_types.png}

### 2023-10-17 visions.qmd
Prep for submission

The Cycle Route Uptake and Scenario Estimation (CRUSE) Tool presented in the paper is the first strategic cycle network planning tool of this level of sophistication to the best of our knowledge. The inclusion of multiple trip types, including travel to work and education from official sources, and simulated trips for other purposes, is a world first for a national tool.
The tool required substantial methodological development, including the development of a new R package (`simodels`, for modelling origin-destination data with spatial interaction models).
The tool is already having major impacts in Ireland and looks set to transform the practice of strategic cycle network planning in Ireland.

>>>>

The Cycle Route Uptake and Scenario Estimation (CRUSE) Tool presented in the paper received funding from the EU via Transport Infrastructure Ireland (TII), with funding in the region of €200k.

This is the first strategic cycle network planning tool of this level of sophistication to the best of our knowledge. The inclusion of multiple trip types, including travel to work and education from official sources, and simulated trips for other purposes, is a world first for a national tool.
The tool required substantial methodological development, including the development of a new R package (`simodels`, for modelling origin-destination data with spatial interaction models).
The tool is already having major impacts in Ireland and looks set to transform the practice of strategic cycle network planning in Ireland.
